\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Improve the specific meaning of "proxy".

Technically, a proxy is any computer or service that allows its users to make indirect network connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper and more generally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.

>>>>

The word ``proxy'' has a specific meaning in the context of a Tor connection.
Generally, a proxy is any computer or service that allows its users to make indirect network connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
